\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}

\title{DevNavigator Project Status}
\author{}
\date{March 28, 2026}

\begin{document}
\maketitle

\section*{Overview}
This document summarizes what has been completed so far in the DevNavigator project, step by step, based on the current workspace state.

\section*{Step by Step Progress}
\begin{enumerate}
  \item A Docker setup was added for the Node entrypoint. The Dockerfile uses \texttt{node:18}, copies the project into \texttt{/app}, conditionally runs \texttt{npm install} if \texttt{package.json} exists, and starts \texttt{index.js}.

  \item A C++ email sending module was added. The project now includes \texttt{cpp\_crawler/include/email\_sender.h} and \texttt{cpp\_crawler/src/email\_sender.cpp}.

  \item The crawler entrypoint was updated. The file \texttt{cpp\_crawler/src/main.cpp} now starts the application, prints a startup message, and calls the database-driven email processing function using \texttt{../database/devnav.db}.

  \item SQLite support was wired into the CMake build. The build now requires SQLite and links against \texttt{SQLite::SQLite3}.

  \item libcurl SMTP support was added for real email delivery. The CMake file now also requires CURL and links against \texttt{CURL::libcurl}.

  \item The email sender now uses environment-based SMTP configuration. It reads values such as \texttt{SMTP\_URL}, \texttt{SMTP\_USERNAME}, \texttt{SMTP\_PASSWORD}, \texttt{SMTP\_FROM}, and optional flags for TLS behavior and verbose logging.

  \item The database email-processing loop is implemented. The code opens the SQLite database, selects up to 50 rows from a \texttt{contacts} table where consent is granted and the message has not yet been sent, sends each email, and updates the row to set \texttt{sent = 1} after successful delivery.

  \item The email message content was updated to describe the current product direction. The outgoing subject now says that a new children's learning app is being launched, and the body explains that the app teaches children through blog-style educational content covering information, culture, stories, religion, and interactive pop-up features.

  \item The C++ project was configured and built successfully. The current build output includes the executable \texttt{cpp\_crawler/build/devnavigator}.
\end{enumerate}

\section*{Current Files of Interest}
\begin{itemize}
  \item \texttt{Dockerfile}
  \item \texttt{index.js}
  \item \texttt{cpp\_crawler/CMakeLists.txt}
  \item \texttt{cpp\_crawler/src/main.cpp}
  \item \texttt{cpp\_crawler/src/email\_sender.cpp}
  \item \texttt{cpp\_crawler/include/email\_sender.h}
  \item \texttt{database/devnav.db}
\end{itemize}

\section*{What Is Still Missing}
\begin{itemize}
  \item The SQLite database file currently exists, but it appears empty. There is no confirmed \texttt{contacts} table or sample data in the current workspace state.

  \item No live SMTP credentials are stored in the project. The code is ready to use them from environment variables, but it has not been tested against a real mail server in this workspace.

  \item The crawler and parser source files are still empty, so the larger crawling pipeline has not been implemented yet.

  \item There are currently two similar header names in the include directory: \texttt{email\_sender.h} and \texttt{emailsender.h}. This should likely be cleaned up later to avoid confusion.
\end{itemize}

\section*{How To Run The Current C++ Build}
\begin{enumerate}
  \item Configure the build:

  \texttt{cmake -S cpp\_crawler -B cpp\_crawler/build}

  \item Build the executable:

  \texttt{cmake --build cpp\_crawler/build}

  \item Run it with SMTP environment variables set:

  \texttt{SMTP\_URL="smtp://smtp.example.com:587" \\
  SMTP\_USERNAME="your-user" \\
  SMTP\_PASSWORD="your-pass" \\
  SMTP\_FROM="you@example.com" \\
  SMTP\_USE\_TLS=1 \\
  ./cpp\_crawler/build/devnavigator}
\end{enumerate}

\section*{Status Summary}
The project now has a working C++ build, SQLite linkage, libcurl SMTP linkage, an email-processing executable entrypoint, and a custom outreach message for the children's learning app launch. The main remaining work is database setup, real contact data, SMTP credential configuration, and implementation of the unfinished crawler and parser components.

\end{document}
